Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-18 Ben_Manuscripts/structure_paper/Draft.tex
More comments.

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment (see section~\ref{method:xrd}). We tested systems built with 5 columns
  per pore in the parallel displaced and sandwiched configurations at 300 K in the 
  ordered and disordered basins. We generated simulated patterns using the equilibrated
  portion of each simulation trajectory. There are two important factors to take into
  account when looking at differences between experimental XRD and simulated XRD. First,
  the simulated diffraction patterns have some noise, especially along the $q_z$ axis 
  at $q_r$=0, which is where several of the more interesting features are located. This
  is due to the angle averaging of the 3D structure factor around the $q_z$-axis, meaning
  there are fewer samples as  $q_r$ approaches 0. The amount of samples to converge along
  the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}. 
  More importantly, our simulations do not appear to be long enough to sample truly 
  independent configurations within their respective metastable basins (See 
  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the
  results of the XRD. The simulated patterns generated for all systems studied are shown
  and compared to experiment in Figure~\ref{fig:XRDsim}.

@@

			\begin{subfigure}{\textwidth}
				\centering
			    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.png}
	\end{subfigure}	
	\caption{Simulated XRD patterns show some qualitative agreement with experiment. Shown is a 
	comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
	disordered basin (d) Parallel displaced, ordered basin and (e) Parallel displaced, disordered basin 
	configurations with (c) experimental WAXS. 	In all cases, R-pores, R-alkanes and R-$\pi$ are 
	present to some degree. R-spots is also present, however it is generally partially covered by the
	broad R-$\pi$ reflection. Quantitative comparisons of the relative intensities of reflections of
	interest are presented in Table~\ref{table:relative_inensities_300K}. In both XRD patterns generated
	from parallel displaced patterns, there is a faint line across $q_z \sim 0.7~$\AA$^{-1}$, half
	the simulated value of R-$\pi$. Although it does not cross through $q_r = 0$~\AA$^{-1}$, it is at 
	the same $q_z$ value where we expect R-double to be present. Still, R-double is not fully reproduced
	in any of the simulated patterns.}~\label{fig:XRDsim} 
  \end{figure}

  The simulated XRD patterns show moderate agreement with experiment. There 
  are key qualitative and quantitative differences between the experimental and simulated
  locations and intensities of each major reflection. We measured the intensity and location
  of each simulated reflection relative to its experimental counterpart 
  (Table~\ref{table:relative_inensities_300K}). Our methods for measuring the intensity of
  each reflection are presented in section S-\ref{S-section:xrd_intensities}.

@@

%  \begin{table}[h]
%  \centering
%  \begin{tabular}{c|cccccccccc}
%  \toprule
% 		   & \multicolumn{5}{c}{Configuration} \\
%  \hline
%           &\multicolumn{2}{c}{}            & \multicolumn{2}{c}{}          & \multicolumn{2}{c}{Parallel} & \multicolumn{2}{c}{Disordered} & \multicolumn{2}{c}{Disordered}         \\
%           & \multicolumn{2}{c}{Experiment} & \multicolumn{2}{c}{Sandwiched} & \multicolumn{2}{c}{Displaced} & \multicolumn{2}{c}{Sandwiched}  & \multicolumn{2}{c}{Parallel Displaced} \\
%  Reflection & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) \\
%  \midrule
%  R-alkanes  & 1.0  & 1.4  & 1.0  & 1.4 & 1.0 & 1.4 & 1.0 & 1.4 & 1.0 & 1.4  \\  
%  R-spots    & 1.3  & 1.4  & 1.3  & 1.4 & 1.2 & 1.4 & 1.1 & 1.4 & 1.2 & 1.4  \\
%  R-$\pi$    & 2.8  & 1.7  & 44.0 & 1.4 & 7.7 & 1.4 & 8.4 & 1.4 & 10.1& 1.4  \\
%  R-double   & 0.9  & 0.85 & --   &  -- & --  & --  & --  & --  &  -- & --   \\ 
%  \bottomrule
%  \end{tabular}
%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
%  does not appear in any patterns, and thus has no measurable intensity.}
%  \label{table:relative_inensities_300K} 
%  \end{table}

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 12.3       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

%    \begin{table}[h]
%  \centering
%  \begin{tabular}{c|ccccc}
%  \toprule
% 		   & \multicolumn{5}{c}{Configuration} \\
%  \hline
%             &\multicolumn{2}{c}{}     &            & Parallel  & Disordered & Disordered         \\
%  Reflection & \multicolumnExperiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
%  \midrule
%  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
%  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
%  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
%  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
%  \bottomrule
%  \end{tabular}
%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
%  does not appear in any patterns, and thus has no measurable intensity.}
%  \label{table:relative_inensities_300K} 
%  \end{table}

@@

%  We quantified the numerical discrepancies present when comparing the relative intensities
%  of each reflection of interest between experimental and simulated patterns. 
%  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
%  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
%  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
%  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
%  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
%  %MRS10: weird transition between these two; it's a result that interrupts the discussion of methods.
%  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
%  identified spots based on visual inspection. 
%  %MRS10: what criteria were used?  Need to provide what was used to make the decision.
%If the spots were not easily discernible, then the 
%  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
%  R-$\pi$, as that is where it appears experimentally. The intensity of R-spots is slightly
%  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
%  agrees with experiment. There is no R-double intensity to be measured. %MRS10: specific where no R-double intensity was measured. None of the simulations, correct?
%Figures are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements. %MRS10: Specify what figures clarify what things.  Also, use active voice in this section.

@@

  We normalized the experimental and simulated diffraction patterns so that the average
  intensity within R-alkanes is equal to 1 because we believe that R-alkanes is the
  experimental feature most likely to be reproduced by our simulations.
  %BJC11: could add some support of this statement - perhaps a reference to the original
  % GAFF forcefield paper? Need to actually check it though.

  R-alkanes appears close to its expected location. In all cases, the maximum intensity
  of R-alkanes appears at a $|\mathbf{q}|$ value only slightly higher than experiment. 
  We expect that the exact location of R-alkanes will not be perfect in our simulations
  since the simulated diffraction patterns are interpolated between a finite number of
  bins in each frequency dimension. We can achieve higher resolution with a larger
  system size, however we are satisfied with the packing distances shown by our simulations.
  %BJC11: I could integrate a 3D correlation function to get a better value

@@

  R-pores is about 4 times more intense than experiment in all simulated systems. We
  hypothesize that this is primarily due to the relatively perfect infinite hexagonal
  array of pores in the simulated systems. In the real system, periodicity of the 
  hexagonal array is disrupted by misalignment of the crystalline domains and the
  pore-to-pore distances fluctuate more over long time scales. 
  % BJC11: Using simple systems, I can show that more highly fluctutating pore-to-pore
  % distances will decrease the intensity of R-pores. I don't think its worth getting
  % into in the main text. It's the same idea as how increased z-noise decreases the intensity of R-pi
  % BJC11: I also think that domain misalignment in the z-direction contributes. If you
  % imagine a hexagonal array of pores aligned along the z-axis, then rotate that axis
  % so it has an x and y component, then there will be constructive interference perpendicular
  % to that axis at non-zero qz values. That is why R-pores is arced. It's a different
  % type of broadening than R-pi - I think
  % BJC11: I don't think a deep dive into this is worth it. It's dependent on things
  % unrelated to the actual pore structure.

  We are not concerned with exactly reproducing the intensity of R-pores since it is a 
  product of long distance correlations between pores. We are primarily concerned with
  the structure within pores which is better described by reflections at higher 
  $|\mathbf{q}|$ values.

  The location of the leading peak of R-pores is geometrically related to the average 
  distance between pores. However, there is uncertainty in its exact location because
  the Fourier bin size is so large. We can measure the average distance between columns
  with more precision in real space (See Section~\ref{method:pore_spacing}). We showed
  that we achieve experimentally consistent pore spacings in our simulations in 
  Section~\ref{section:section:mon_per_pore}.

@@

  The intensity of R-spots is close to experiment when generated from any of our
  simulated systems. The appearance of R-spots is inconspicuous in most cases so we
  assumed that the location of R-spots, in terms of $|\mathbf{q}|$ would coincide with
  that of R-alkanes, and that it's $q_z$ location should be roughly in line with 
  R-double (half the $q_z$ location of R-$\pi$) as it appears in the experimental pattern.
  We measured the intensity of R-spots by radially integrating the simulated
  diffraction pattern between $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$ (between
  4 and 4.5 $\AA$ in real space) and then locating and recording the intensity of the 
  appropriate peaks in the resulting distribution.

  R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
  Previous literature has attributed the spots in this particular WAXS dataset as 
  the product of tilted alkane chains~\cite{feng_scalable_2014}. Here we refute 
  that explanation and show that the tails do not tilt, but rather pack in a 
  hexagonal array.

  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
  configuration at 280K. Many force fields do not obtain the correct equilibrium structure
  at precisely the experimental temperature. Wang et al. highlighted the shortcoming of 
  some of the most popular protein force field in predicting the temperature dependence 
  of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
  our membrane system, simulated at 300K, is under-structured in the tail region compared
  to the experimental structure at 300K. We found that lowering the temperature better 
  resolved R-spots (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' 
  temperature might indeed be too high, understabilizing structure.

  Evidence from the simulations strongly suggests that the R-spots signal is not a 
  result of alkane chain tilt. We measured the tilt angle of the alkane chains of
  the 280K system and showed that it equilibrates to an average tilt angle of
  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots.

  Although the monomer tails do not tilt, R-spots still originates from 
  them. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern with the remaining atoms, we were able to isolate the
  cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).

  %BJC11: need to rephrase -- "strongly suggests" used two paragraphs prior
  The evidence strongly suggests that R-spots occurs because tails pack 
  together hexagonally. We plotted the center of masses of the first four tail 
  atoms of all tails (Figure \ref{fig:centroids}). We measured the angle between
  each center of mass and its nearest neighbor center of masses with respect to
  the $xy$ plane of the membrane. We see distinct peaks in the distribution of
  these angles located ca. $-60\degree$, $0\degree$, and $60\degree$ which is
  consistent with a hexagonally packed configuration (Figure~\ref{fig:layered_tails}). 
  %MRS10: is it importat that the ordering dies off? IF there is ordering, it will show in the spectra, and it doesn't matter that it dies off in other parts of the spectra.
  %BJC10: I only addressed this because Matt wanted a more thorough characterization of tail order 
  This ordering dies off at the tail ends, where there is more space to fill 
  causing them to pack nearly isotropically. See Section~S-\ref{S-tail_packing}
  for a more detailed explanation of the calculation and packing distributions
  generated from different sections of the tails.

@@

  The position, shape and intensity of R-$\pi$, generated from simulations at 300K, are 
  qualitatively and quantitatively different than experiment. The reflections appear
  at lower $q_z$ values, they are more intense and the shape of its cross-sections, 
  especially in the $q_r$ direction are different relative to the experimental system
  (See Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the simulated
  XRD generated from the ordered parallel displaced configuration as an example). In 
  this section, we explore the various contributions to these discrepancies, and use what
  we've learned to speculate on improvements to our initial configurations and simulation
  procedures.

>>>>

  We 
  %MRS12: sounds too much like structure refinement
  %further refined our structural understanding 
  can better understand the structure of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment (see section~\ref{method:xrd}). We tested systems built with 5 columns
  per pore in the parallel displaced and sandwiched configurations at 300 K in the 
  ordered and disordered basins,
  %MRS12: added
  as those were the most consistent with the most unambiguous X-ray diffraction patterns, the pore-to-pore spacing and the stacking distance.
We generated simulated patterns using the 
  %MRS12: maybe refer to part of methods where we determined which ones were equilibrated?  Also, maybe say locally equilibrated? Since we know it might be only metastable. 
equilibrated
  portion of each simulation trajectory. There are two important factors to take into
  account when looking at differences between experimental XRD and simulated XRD. First,
  the simulated diffraction patterns have some noise, especially along the $q_z$ axis 
  at $q_r$=0, which is where several of the more interesting features are located. This
  is due to the angle averaging of the 3D structure factor around the $q_z$-axis, meaning
  there are fewer samples as  $q_r$ approaches 0. The amount of samples 
  %MRS12: added
  required to
  to converge along
  the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}. 
  More importantly, our simulations do not appear to be long enough to sample truly 
  independent configurations within their respective metastable basins (see 
  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the
  results of the XRD. The simulated patterns generated for all systems studied are shown
  and compared to experiment in Figure~\ref{fig:XRDsim}.

@@

			\begin{subfigure}{\textwidth}
				\centering
			    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.png}
	\end{subfigure}	
	\caption{Simulated XRD patterns show some qualitative agreement with experiment. Shown is a 
	comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
	disordered basin (d) Parallel displaced, ordered basin and (e) Parallel displaced, disordered basin 
	configurations with (c) experimental WAXS. 	In all cases, R-pores, R-alkanes and R-$\pi$ are 
	present to some degree. R-spots is also present, however it is generally partially covered by the
	broad R-$\pi$ reflection. Quantitative comparisons of the relative intensities of reflections of
	interest are presented in Table~\ref{table:relative_intensities_300K}. In both XRD patterns generated
	from parallel displaced patterns, there is a faint line across $q_z \sim 0.7~$\AA$^{-1}$, half
	the simulated value of R-$\pi$. Although it does not cross through $q_r = 0$~\AA$^{-1}$, it is at 
	the same $q_z$ value where we expect R-double to be present. Still, R-double is not fully reproduced
	in any of the simulated patterns.}~\label{fig:XRDsim} 
        %MRS12: I would repeat the labels from figure 3.  Minimum, need to refer back to that figure so they know where to find the definitions of the lables. 
  \end{figure}

  The simulated XRD patterns show moderate agreement with experiment. There 
  are key qualitative and quantitative differences between the experimental and simulated
  locations and intensities of each major reflection. The integrated intensity and location
  of each simulated reflection relative to its experimental counterpart are shown in  
  Table~\ref{table:relative_intensities_300K}. Our approach for measuring the intensity of
  each reflection are described in section S-\ref{S-section:xrd_intensities}. %MRS12: should that be in Methods instead of suporting?  Not sure.

@@

%  \begin{table}[h]
%  \centering
%  \begin{tabular}{c|cccccccccc}
%  \toprule
% 		   & \multicolumn{5}{c}{Configuration} \\
%  \hline
%           &\multicolumn{2}{c}{}            & \multicolumn{2}{c}{}          & \multicolumn{2}{c}{Parallel} & \multicolumn{2}{c}{Disordered} & \multicolumn{2}{c}{Disordered}         \\
%           & \multicolumn{2}{c}{Experiment} & \multicolumn{2}{c}{Sandwiched} & \multicolumn{2}{c}{Displaced} & \multicolumn{2}{c}{Sandwiched}  & \multicolumn{2}{c}{Parallel Displaced} \\
%  Reflection & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) \\
%  \midrule
%  R-alkanes  & 1.0  & 1.4  & 1.0  & 1.4 & 1.0 & 1.4 & 1.0 & 1.4 & 1.0 & 1.4  \\  
%  R-spots    & 1.3  & 1.4  & 1.3  & 1.4 & 1.2 & 1.4 & 1.1 & 1.4 & 1.2 & 1.4  \\
%  R-$\pi$    & 2.8  & 1.7  & 44.0 & 1.4 & 7.7 & 1.4 & 8.4 & 1.4 & 10.1& 1.4  \\
%  R-double   & 0.9  & 0.85 & --   &  -- & --  & --  & --  & --  &  -- & --   \\ 
%  \bottomrule
%  \end{tabular}
%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
%  does not appear in any patterns, and thus has no measurable intensity.}
%  \label{table:relative_intensities_300K} 
%  \end{table}

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 12.3       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  %MRS12: question: is the normalization for the simulated systems the same, no matter if disordered, etc.  If not chosen to be exactly the same, how different are they? 
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes in each pattern equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any simulated patterns, and thus has no measurable intensity.}
  \label{table:relative_intensities_300K} 
  \end{table}

%    \begin{table}[h]
%  \centering
%  \begin{tabular}{c|ccccc}
%  \toprule
% 		   & \multicolumn{5}{c}{Configuration} \\
%  \hline
%             &\multicolumn{2}{c}{}     &            & Parallel  & Disordered & Disordered         \\
%  Reflection & \multicolumnExperiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
%  \midrule
%  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
%  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
%  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
%  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
%  \bottomrule
%  \end{tabular}
%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
%  does not appear in any patterns, and thus has no measurable intensity.}
%  \label{table:relative_intensities_300K} 
%  \end{table}

@@

%  We quantified the numerical discrepancies present when comparing the relative intensities
%  of each reflection of interest between experimental and simulated patterns. 
%  Table~\ref{table:relative_intensities_300K} shows the relative intensities of each reflection for 
%  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
%  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
%  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
%  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
%  %MRS10: weird transition between these two; it's a result that interrupts the discussion of methods.
%  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
%  identified spots based on visual inspection. 
%  %MRS10: what criteria were used?  Need to provide what was used to make the decision.
%If the spots were not easily discernible, then the 
%  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
%  R-$\pi$, as that is where it appears experimentally. The intensity of R-spots is slightly
%  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
%  agrees with experiment. There is no R-double intensity to be measured. %MRS10: specific where no R-double intensity was measured. None of the simulations, correct?
%Figures are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements. %MRS10: Specify what figures clarify what things.  Also, use active voice in this section.

@@

  We normalized the experimental and simulated diffraction patterns so that the average
  intensity within R-alkanes is equal to 1 because we believe that R-alkanes is the
  experimental feature most likely to be reproduced by our simulations. 
  %BJC11: could add some support of this statement - perhaps a reference to the original
  % GAFF forcefield paper? Need to actually check it though.
  %MRS12: first pass.  
  We reach this conclusion because alkane
  parameters in GAFF and AMBER forcefields are generally reproduce data well.~\cite{original_gaff_paper} 
  %MRS12: Citation is: https://doi.org/10.1002/jcc.20035  could also cite: https://pubs.acs.org/doi/pdf/10.1021/ct200731v
  %MRS12: below - say what appears close means?  radius of max is X vs Y.
  R-alkanes appears close to its expected location. In all cases, the maximum intensity
  of R-alkanes appears at a $|\mathbf{q}|$ value only slightly higher than experiment. 
  %MRS12: different pass? Though need to specify WHAT the error is.  Can't be intensity, since that is what we are normalizing by, so is it LOCATION of the intensity?  Also, need to verify the statement is correct.  Could still good languange if the conclusion was that the binning error was similar in size to errors in the location R-alkane.
  The error in the simulated diffraction patterns is less that the error due binning in eack frequency direction, so was not further investigated. 
  %We expect that the exact location of R-alkanes will not be perfect in our simulations
  %since the simulated diffraction patterns are interpolated between a finite number of
  %bins in each frequency dimension. 
  %We can achieve higher resolution with a larger
  %system size, however we are satisfied with the packing distances shown by our simulations.
  %BJC11: I could integrate a 3D correlation function to get a better value.
  %MRS12: saying ``we are satisfied'' opens to claims that reviwers say ``well, I'm not''.  Pass at this above.

@@

  R-pores is about 4 times more intense than experiment in all simulated systems. We
  hypothesize that this is primarily due to the relatively perfect infinite hexagonal
  array of pores in the simulated systems. In the real system, periodicity of the 
  hexagonal array is disrupted by misalignment of the crystalline domains and the
  pore-to-pore distances fluctuate more over long time scales. 
  % BJC11: Using simple systems, I can show that more highly fluctutating pore-to-pore
  % distances will decrease the intensity of R-pores. I don't think its worth getting
  % into in the main text. It's the same idea as how increased z-noise decreases the intensity of R-pi
  % BJC11: I also think that domain misalignment in the z-direction contributes. If you
  % imagine a hexagonal array of pores aligned along the z-axis, then rotate that axis
  % so it has an x and y component, then there will be constructive interference perpendicular
  % to that axis at non-zero qz values. That is why R-pores is arced. It's a different
  % type of broadening than R-pi - I think
  % BJC11: I don't think a deep dive into this is worth it. It's dependent on things
  % unrelated to the actual pore structure.
  % MRS12:  Agreed. Rephrased a bit.
  The agreement in intensity in R-pores obtained here is sufficient for this study because this intensity is primarily controlled by longer-range organization that cannot be captured by simulation of only 4 pores and because we are concered with the with the structure of the individual pores themselves.

  The location of the leading peak of R-pores is directly related to the average 
  distance between pores. However, there is substatial uncertainty in the exact location 
  relative to the bin size used for the Fourier space transformation. We can instead 
  measure the average distance between columns
  with more precision in real space (See Section~\ref{method:pore_spacing}). We showed
  that we achieve experimentally consistent pore spacings in our simulations in 
  Section~\ref{section:section:mon_per_pore}.

@@

  The intensity of R-spots is close to experiment when generated from any of our
  simulated systems. 
  Because the R-spots reflection is difficult to distinguish visually as it appears 
  at the same $|\mathbf{q}|$ as R-alkanes, we calculate 
  the intensity of R-spots by assuming that its $q_z$ location should be roughly in line with 
  the experimental R-double, half the $q_z$ distance of R-$\pi$).
  %The appearance of R-spots is inconspicuous in most cases so we
  %assumed that the location of R-spots, in terms of $|\mathbf{q}|$ would coincide with
  %that of R-alkanes, and that it's $q_z$ location should be roughly in line with 
  %R-double (half the $q_z$ location of R-$\pi$) as it appears in the experimental pattern.
  We measured the intensity of R-spots by radially integrating the simulated
  diffraction pattern between $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$ (between
  4 and 4.5 $\AA$ in real space) and then locating and recording the intensity of the 
  appropriate peaks in the resulting distribution.

  %MRS12: here I'm going to break the rule of the thesis statement, since it reads strangely to have thesis, contradition, repeat thesis, there isn't any evidence. But it flows OK this way.   
  %R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
  Previous literature has attributed the R-spots reflection in this particular WAXS dataset as 
  the result of tilted alkane chains~\cite{feng_scalable_2014}. 
  %Here we refute that explanation and show that the 
  We measured the tilt angle of the alkane chains of
  the 280K system and found that it equilibrates to an average tilt angle of
  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots. Similar lack of more than a statistically negligible tilt occured when 
  we performed the simulations with a number of other starting configurations, obtaining similar results.%MRS12: I know we discussed this earlier; there were a number of things that were done to verify this results was consistent, and I think that a rief summary would help.

  In order to more clearly identify the structural reasons for R-spots, we equilibrated an ordered basin sandwiched 
  configuration at 280K to moderately increase the order and therefore intensity. 
  Many force fields do not obtain the correct equilibrium structure
  at precisely the experimental temperature. Wang et al. highlighted the shortcoming of 
  some of the most popular protein force field in predicting the temperature dependence 
  of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
  our membrane system, simulated at 300K, is under-structured in the tail region compared
  to the experimental structure at 300K. We found that lowering the temperature indeed better 
  resolved R-spots (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' 
  temperature might indeed be too high, understabilizing structure.

  The Evidence from the simulations strongly suggests that the R-spots signal
 is not a 
  result of alkane chain tilt.

  The evidence from simulations strongly suggest that the source of
  the R-spots reflection is packing of the tails in a hexagonal array.
  First, we demonstrate R-spots comes primarily from the tails, by
  removing all non-tail atoms from the trajectory and simulating the
  XRD diffraction pattern with the remaining atoms, which preserves
  R-spots(Figure~\ref{fig:tails_rzplot}).  Next, we plotted the center
  of masses of the first four tail atoms of all tails (Figure
  \ref{fig:centroids}). We measured the angle between each center of
  mass and its nearest neighbor center of masses with respect to the
  $xy$ plane of the membrane. We see distinct peaks in the
  distribution of these angles located ca. $-60\degree$, $0\degree$,
  and $60\degree$ which is consistent with a hexagonally packed
  configuration (Figure~\ref{fig:layered_tails}).  This ordering is
  primarily in the parts of the tail proxmal to the heads, and dies
  off at the tail ends, where there is more space to fill causing them
  to pack nearly isotropically. See Section~S-\ref{S-tail_packing} for
  a more detailed explanation of the calculation and packing
  distributions generated from different sections of the tails.

@@

  The position, shape and intensity of R-$\pi$, generated from simulations at 300K, are 
  qualitatively similar to experiment, but have significant quantitative differences. The reflections appear
  at lower $q_z$ values, they are more intense, and the shape of its cross-sections, 
  especially in the $q_r$ direction are different relative to the experimental system.
  For comparison, see Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the simulated
  XRD generated from the ordered parallel displaced configuration as an example. In 
  this section, we explore the various contributions to these discrepancies, and use this information to 
  speculate on what reasonable differences in the simulations could explain the discrepancies.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
  The maximum intensity of R-$\pi$ generated from simulations of the ordered
  parallel displaced configuration is 3 times larger than experiment. The $q_r$
  cross-section of R-$\pi$ ((a) and (b)) is qualitatively different between 
  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
  the FWHM (full width at half maximum) of the simulated pattern agrees with experiment within error. However
  the fit to the simulated data is affected by the three sharp peaks which appear
  near $q_r$ = 0. The $q_z$ cross-sections of R-$\pi$ ((c) and (d)) are 
  qualitatively similar. Each fits a Lorentzian profile well, however the FWHM
  of the simulated cross-section (d) is 48\% larger than the experimental 
  cross-section. Additionally, peak of the simulated $q_z$ cross-section is 
  located at a somewhat lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
  \end{figure}
